Identification of protoneutron star g-modes in gravitational-wave data

### 2020-09-10 results.tex
updated aLIGO all wvf plots & results

For each of the noise realisations, we reconstruct the ratio time series {$r_i$}
of length $N$ and compare it to ratio {$r_i^0$} derived from
the PNS mass and radius generated by the simulation code that produced {\texttt s20S}.

@@

    Simulation & \texttt{s11} & \texttt{s15} & \texttt{s15S} & \texttt{s15G} & \texttt{s20} & \texttt{s20S} & \texttt{s25}  & \texttt{s40}
    \\   
    \hline
    aLIGO char. distance & 7     &            &                &               &   15.6           &    11.3   &  8.9             &  11.5
    \\ 
    \hline
    SNR in aLIGO         & 19.5 & 55.4        & 59.0          &   60.0        & 34.3         &   35.8          & 116.5         & 98.5
    \\
    \hline
    \hline
    CE2  max. distance  &      &            &                &               &              &                 &               & 
    \\
    \hline
    SNR in CE2      &      &            &                &               &              &                 &               &
    \\
    \hline
    \hline
  \end{tabular}
  \caption{%%
    Matched filter signal-to-noise ratio (SNR) of the simulated waveforms for
    the different GW detectors considered in this study. The source is located
    at 10 kpc and is optimally oriented with respect to the detector.
    %%
  }
  \label{Tab:results}
\end{table}

>>>>

For each of the noise realisations, we reconstruct the ratio time series {$r_i$}
of length $N$ starting from the left side of the spectrogram and constraining the beginning of the
track to be smaller than \unit[200]{Hz}. The reconstructed ratio is then compare to the ``true'' ratio
{$r_i^0$} derived from the PNS mass and radius generated by the simulation code that produced {\texttt s20S}.

@@

    Simulation & \texttt{s11} & \texttt{s15} & \texttt{s15S} & \texttt{s15G} & \texttt{s20} & \texttt{s20S} & \texttt{s25}  & \texttt{s40}
    \\   
    \hline
    aLIGO char. & 7  &      26      &    25         &      21       &   16         &    11         &  9           &  12
    \\
    distance (kpc) & & & & & & & &
    \\ 
    \hline
    SNR in aLIGO         & 19.5 &    55.4    &    59.0       &      60.0     &   34.3       &    35.8          & 116.5         & 98.5
    \\
    \hline
    \hline
    CE2  char.  &      &            &                &               &              &                 &               & 
    \\
    distance (kpc) & & & & & & & &
    \\
    \hline
    SNR in CE2      &      &            &                &               &              &                 &               &
    \\
    \hline
    \hline
  \end{tabular}
  \caption{%%
    Matched filter signal-to-noise ratio (SNR) of the simulated waveforms for
    the different GW detectors considered in this study. The source is located
    at 10 kpc and is optimally oriented with respect to the detector.
    %%
  }
  \label{Tab:results}
\end{table}
